Additional analysis

### 2020-09-30 README.Rmd
Add badges

>>>>

[![NVSQ DOI](https://img.shields.io/badge/NVSQ%20DOI-Forthcoming-brightgreen)](#) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FFG53W-blue)](https://dx.doi.org/10.17605/OSF.IO/FG53W) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4058987.svg)](https://doi.org/10.5281/zenodo.4058987)

![Preregistered](img/preregistered_large_color.png) &emsp; ![Open data](img/data_large_color.png) &emsp; ![Open](img/materials_large_color.png)
